Verifying the \shaThree\ Implementation from \openssl\ with the Software Analysis Workbench

### 2022-06-14 paper/paper.tex
Add Parker's orcid

\begin{document}
%
\title{Verifying the \shaThree\ Implementation from \openssl\ with the Software Analysis Workbench}
%
%\titlerunning{Abbreviated paper title}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{
  Parker Hanson\inst{1} \and
  Benjamin Winters\inst{1} \and
  Eric Mercer\inst{1}\orcidID{0000-0002-2264-2958} \and
  Brett Decker\inst{1}
}
%
\authorrunning{P. Hanson et al.}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{
  Brigham Young University, Provo UT 84602, USA
}
%
\maketitle              % typeset the header of the contribution
%
\begin{abstract}
\input{abstract}
\keywords{Formal Verification \and Cryptography \and \shaThree \and \cryptol \and \saw.}
\end{abstract}

>>>>

\begin{document}
%
\title{Verifying the \shaThree\ Implementation from \openssl\ with the Software Analysis Workbench}
%
%\titlerunning{Abbreviated paper title}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{
  Parker Hanson\inst{1}\orcidID{0000-0003-0893-0096} \and
  Benjamin Winters\inst{1} \and
  Eric Mercer\inst{1}\orcidID{0000-0002-2264-2958} \and
  Brett Decker\inst{1}
}
%
\authorrunning{P. Hanson et al.}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{
  Brigham Young University, Provo UT 84602, USA
}
%
\maketitle              % typeset the header of the contribution
%
\begin{abstract}
\input{abstract}
\keywords{Formal Verification \and Cryptography \and \shaThree \and \cryptol \and \saw.}
\end{abstract}
